### 2018-06-11 ident/docs/draft_4.tex
remove tikz and subfigure from preamble
changes to figures and addition of figure captions for sifigures

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{pifont}
\usepackage{bm}
\usepackage{graphicx}
\usepackage[space]{grffile}
\usepackage{multicol}
\usepackage{array}
\usepackage{tabu}
\usepackage{ragged2e}
\usepackage{setspace}
\usepackage{xr} % package for linking external document references
\usepackage[font=small,labelfont=bf,labelsep=period]{caption}
%\usepackage{subcaption}
%\usepackage[CaptionAfterwards]{fltpage}
\usepackage{subfigure}
\usepackage{lineno}
\linenumbers
\usepackage{tikz}
\def\checkmark{\tikz\fill[scale=0.4](0,.35) -- (.25,0) -- (1,.7) -- (.25,.15) -- cycle;} 
\usepackage[margin=1.0in]{geometry}

@@

	Experimental data (concentration or fluxes) from many physical systems is usually noisy, and sometimes may not contain all requisite information pertaining to the system. When parameters are estimated on the basis of this data, the ability to estimate unique parameter values to satisfy Equation (\ref{eq:stident}) is referred to as practical identifiability. If unique parameter values satisfying Equation (\ref{eq:stident}) can be estimated, then $\theta$ is said to be globally practically identifiable. Whereas, if parameter estimates with quantifiable uncertainties can be found, then $\theta$ is said to be locally identifiable. No unique parameter estimates can be found if $\theta$ is practical non-identifiable.

@@

	\subsection{A method to determine structural and practical identifiability of kinetic models of metabolism}\label{sec:ident}
	In this section, we provide the mathematical framework for \textcolor{red}{identification} of parameters in kinetic models of metabolism. A summary of the methodology in the form of a flow diagram is shown in Figure \ref{fig:ident-flowchart}. As indicated in Figure \ref{fig:ident-flowchart}a, the first step involves the construction of the kinetic model (Equation \ref{eq:kinstoich}) of the metabolic network with $n_r$ reaction fluxes.

@@

	For each flux $v_i$, $i={1, 2, ..., n_r}$, in the kinetic model, let $\mathbf{\theta} \in \mathbb{R}^p$ in Equation (\ref{eq:kinstoich}b). If data from $n_E$ experiments is available for the chosen metabolic network, as stated earlier, for each experiment $j = {1, 2, ..., n_E}$, we assume that all metabolite concentrations ($x\in\mathbb{R}^{n_x}$) and reaction fluxes ($v\in\mathbb{R}^{n_r}$) are measurable. We discuss the implications of relaxing this assumption in the results section. The pertinent information for each experiment $j$ is available as a vector of concentrations and fluxes, $\mathbf{x}_j$ and $\mathbf{v}_j$, respectively (Figure \ref{fig:ident-flowchart}b).

	In order to establish the practical identifiability of kinetic parameters for each flux $v_i$, $i={1, 2, ..., n_r}$, we describe a computer algebra-based method. The primary use of the computer algebra system is to obtain closed-form expressions for each parameter in $\mathbf{\theta} \in \mathbb{R}^p$ for each flux $v_i$ (Figure \ref{fig:ident-flowchart}b). This is done by first selecting a combination of $p\le n_E$ experimental data. The fluxes and concentrations from $p$ different experiments are then used to formulate a system of nonlinear algebraic equations in $\mathbb{R}^p$ for each flux $v_i$, shown in Equation (\ref{eq:nonlineq}). 
	\begin{align}\label{eq:nonlineq}
	v_{i, j} = f_j(\mathbf{x}_j,\mathbf{\theta}, \mathbf{u}_j) && \forall j=\{1, 2, ..., p\}\subset\{1, 2, ..., n_E\}
	\end{align}
	Here, $v_{i,j}$ refers to the flux $v_i$ obtained from experiment $j$. $\mathbf{x}_j$ and $\mathbf{u}_j$ are the vector of metabolite and other input concentrations from each experiment $j$, and $\mathbf{\theta}$ is a vector in $\mathbb{R}^p$, whose elements are denoted by $\theta_k$.

	Each equation in (\ref{eq:nonlineq}), indicated by the index $j$, corresponds to the kinetic rate law expression $f(x, \theta, u)$ for each $v_i$, $i={1, 2, ..., n_r}$, described in Equation (\ref{eq:kinstoich}b), written for concentrations ($\mathbf{x}_j$, $\mathbf{u}_j$) and fluxes ($v_{i,j}$) obtained from experiment $j$. Solving the system in Equation (\ref{eq:nonlineq}) results in $\mathbb{R}^p$ nonlinear expressions for each parameter $\theta_k$ in $\theta \in \mathbb{R}^p$ (Equation \ref{eq:theta-eq}), where $N(\mathbf{v}_i, \mathbf{x}, \mathbf{u})$ is the numerator of $g$, and $D(\mathbf{v}_i, \mathbf{x}, \mathbf{u})$ is the denominator of $g$ (Figure \ref{fig:ident-flowchart}b). Note that $\mathbf{v}_i$, $\mathbf{x}$ and $\mathbf{u}$ are used to denote vector of vectors of fluxes for reaction $i$ ($\mathbf{v}_i$), metabolite ($\mathbf{x}$) and input ($\mathbf{u}$) concentrations, respectively, obtained from $p$ experiments denoted by the index $j = {1, 2, ..., p}$.
	\begin{align}\label{eq:theta-eq}
	\theta_k = g_k(\mathbf{v}_i, \mathbf{x}, \mathbf{u}) = \frac{N_k(\mathbf{v}_i, \mathbf{x}, \mathbf{u})}{D_k(\mathbf{v}_i, \mathbf{x}, \mathbf{u})}
	\end{align}

@@

	\begin{subequations}\label{eq:numerical_opt}
		\begin{align}
		\underset{\theta, \varepsilon}{min} & \sum_{j=1}^{p} \left|\varepsilon_j\right|\\
		& v_{i, j} - f_j(\mathbf{x}_j,\mathbf{\theta}, \mathbf{u}_j) \le \varepsilon_j && j=\{1, 2, ..., p\}\\
		& \theta_l \le \theta_j \le \theta_u && j=\{1, 2, ..., p\}
		\end{align}
	\end{subequations}

	The formulation of the above optimization problem is similar to the least squares problem shown earlier in Equation (\ref{eq:lsqopt}). Notice that the parameter values are bounded above and below by $\theta_u$ and $\theta_l$, respectively. These bounds can be specified to be arbitrarily large to include all possible parameter values.

@@

	The identifiability of each parameter based on each experiment with index $j = {1, 2, ..., n_E}$ is established based on the methodology described in Section \ref{sec:ident} (Figure \ref{fig:ident-flowchart}b), and demonstrated in Section \ref{sec:example}. Subsequently, for any flux $v_i$, and for any combination of $p$ experimental data sets, if the experimental concentrations and fluxes ($\mathbf{x}_j$ and $\mathbf{v}_j$, respectively, where $j = {1, 2,..., p}$) do not satisfy the condition for identifiability for any parameter $\theta_k$ in $\theta\in\mathbb{R}^p$ (Figure \ref{fig:ident-flowchart}b), then at least one of the $p$ experiments needs to be changed to make parameter $\theta_k$ identifiable. Consequently, the corresponding experiment cannot be used for estimating parameter $\theta_k$, and needs to be discarded from the set of all necessary experiments. Furthermore, another experiment from $j = {1, ..., n_E}$ needs to be selected to replace the discarded experiment such that parameter $\theta_k$ is identifiable. This process has to be repeated until all parameters in $\theta\in\mathbb{R}^p$ are identifiable for flux $v_i$. In doing so, we can arrive at a set of $p$ experiments that will always result in practically identifiable parameters for flux $v_i$. Note that if none of the $n_E$ pre-selected experiments satisfy the identifiability condition, then we can design an $(n_E+1)^{th}$ experiment that can replace one of the experiments that causes practical non-identifiability. This analysis can be performed for each flux in a metabolic network independent of all the other fluxes, making it theoretically scalable even to genome-scale models of metabolism.

@@

	\begin{figure}[!tbhp]
		\centering{\includegraphics[width=1.0\textwidth,height=.8\textheight,keepaspectratio]{figures/figure6/v1_kcat_v2_v5_2_v3_1_parameter_dist}}
		\caption{Distribution of predicted parameter values when performing practical identifiability analysis using closed-form solutions for each parameter in flux a) $v_1$, b) $v_2$, c) $v_5$, and d)$v_3$. For $v_1$, we have assumed that enzyme concentration is available and have accordingly identified and estimated $k_1^{cat}$, as opposed to $V_1^{max}$. The parameter values for only the second root of $K_e^{fdp}$ in $v_5$ ($K_e^{fdp}(2)$) is shown, since $K_e^{fdp}(1)$ is not estimated by any combination of two experiments, and $V_e^{max}$ is estimated by all combinations. Only one of the two roots for $v_3$ is shown in panel d. The estimated data for the second root has a similar distribution to that of the first root. Data is generated using the Convenience Kinetic model for allosteric regulation for  $v_3$.}\label{fig:ident_values}
	\end{figure}

@@

	\begin{figure}[!tbhp]
		\centering{\includegraphics[width=0.8\textwidth,height=0.3\textheight, keepaspectratio]{figures/figure6/v3_var_1_2_ck_parameter_value}}
		\caption{Distribution of predicted parameter values when performing practical identifiability analysis using closed-form solutions for each parameter in flux $v_3$. The globally identifiable parameter values of a)  $V_3^{max}$ and $K_3^{fdp}$ when $K_3^{pep}$ is held constant, and b) $V_3^{max}$ and $K_3^{pep}$ when $K_3^{fdp}$ is held constant.}\label{fig:v3_var_ck_values}
	\end{figure}

@@

	\begin{figure}[!tbhp]
		\centering{\includegraphics[width=1.0\textwidth,height=0.9\textheight,keepaspectratio]{figures/figure1/v1_kcat_v2_v5_2_exp_info}}
		\caption{The number of data combination from 21 different in silico experiments that can practically identify each parameter in fluxes a) $v_1$, b) $v_2$, and c) $v_5$ when there is no noise in the input experimental data. The percentage of total combinations of experimental data used for analysis (240 for $v_1$ and $v_2$, and 421 for $v_5$) that can identify each parameter is also specified. $v_1$, $v_2$ and $v_5$ require data from two experiments for analysis. The contribution of different experiment type towards identifying each parameter is shown in the spider plots for d) $v_1$, e) $v_2$ and f) $v_5$. The choice of perturbation chosen for the first experiment (blue) determines the choice of the second perturbation (green) required for identifying the parameters.}\label{fig:ident}
	\end{figure}

>>>>

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{pifont}
\usepackage{bm}
\usepackage{graphicx}
\usepackage[space]{grffile}
\usepackage{multicol}
\usepackage{array}
\usepackage{tabu}
\usepackage{ragged2e}
\usepackage{setspace}
\usepackage{xr} % package for linking external document references
\usepackage[font=small,labelfont=bf,labelsep=period]{caption}
%\usepackage{subcaption}
%\usepackage[CaptionAfterwards]{fltpage}
\usepackage{lineno}
\linenumbers
\usepackage{tikz}
\usepackage[margin=1.0in]{geometry}

@@

	Experimental data (concentration or fluxes) from many physical systems is usually noisy, and sometimes may not contain all requisite information pertaining to the system. When parameters are estimated on the basis of this data, the ability to estimate unique parameter values to satisfy Equation (\ref{eq:stident}) is referred to as practical identifiability. If unique parameter values satisfying Equation (\ref{eq:stident}) can be estimated, then $\theta$ is said to be globally practically identifiable. Whereas, if parameter estimates with quantifiable uncertainties that satisfy Equation (\ref{eq:stident}) can be found, then $\theta$ is said to be locally identifiable. No unique parameter estimates can be found if $\theta$ is practical non-identifiable.

@@

	\subsection{A method to determine structural and practical identifiability of kinetic models of metabolism}\label{sec:ident}
	In this section, we provide the mathematical framework for determining the identifiability of parameters in kinetic models of metabolism. The methodology in shown as a flow diagram in Figure \ref{fig:ident-flowchart}.

@@

	As indicated in Figure \ref{fig:ident-flowchart}a, the first step involves the construction of the kinetic model (Equation \ref{eq:kinstoich}) of the metabolic network with $n_r$ reaction fluxes. For each flux $v_i$, $i={1, 2, ..., n_r}$, in the kinetic model, let $\mathbf{\theta} \in \mathbb{R}^{n_p}$ in Equation (\ref{eq:kinstoich}b). If data from $n_E$ experiments is available for the chosen metabolic network, as stated earlier, for each experiment $j = {1, 2, ..., n_E}$, we assume that all metabolite concentrations ($x\in\mathbb{R}^{n_x}$) and reaction fluxes ($v\in\mathbb{R}^{n_r}$) are measurable. We discuss the implications of relaxing this assumption in the results section. The pertinent information for each experiment $j$ is available as a vector of concentrations and fluxes, $\mathbf{x}_j$ and $\mathbf{v}_j$, respectively (Figure \ref{fig:ident-flowchart}b).

	In order to establish the identifiability of kinetic parameters for each flux $v_i$, $i={1, 2, ..., n_r}$, we describe a computer algebra-based method. The primary use of the computer algebra system is to obtain closed-form expressions for each parameter in $\mathbf{\theta} \in \mathbb{R}^p$ for each flux $v_i$ (Figure \ref{fig:ident-flowchart}b). This is done by first selecting a combination of $n_p\le n_E$ experimental data. The fluxes and concentrations from $n_p$ different experiments are then used to formulate a system of nonlinear algebraic equations in $\mathbb{R}^{n_p}$ for each flux $v_i$, shown in Equation (\ref{eq:nonlineq}). 
	\begin{align}\label{eq:nonlineq}
	v_{i, j} = f_j(\mathbf{x}_j,\mathbf{\theta}, \mathbf{u}_j) && \forall j=\{1, 2, ..., p\}\subset\{1, 2, ..., n_E\}
	\end{align}
	Here, $v_{i,j}$ refers to the flux $v_i$ obtained from experiment $j$. $\mathbf{x}_j$ and $\mathbf{u}_j$ are the vector of metabolite and other input concentrations from each experiment $j$, and $\mathbf{\theta}$ is a vector in $\mathbb{R}^{n_p}$, whose elements are denoted by $\theta_k$.

	Each equation in (\ref{eq:nonlineq}), indicated by the index $j$, corresponds to the kinetic rate law expression $f(x, \theta, u)$ for each $v_i$, $i={1, 2, ..., n_r}$, described in Equation (\ref{eq:kinstoich}b), written for concentrations ($\mathbf{x}_j$, $\mathbf{u}_j$) and fluxes ($v_{i,j}$) obtained from experiment $j$. Solving the system in Equation (\ref{eq:nonlineq}) results in $\mathbb{R}^{n_p}$ nonlinear expressions for each parameter $\theta_k$ in $\theta \in \mathbb{R}^{n_p}$ (Equation \ref{eq:theta-eq}), where $N(\mathbf{v}_i, \mathbf{x}, \mathbf{u})$ is the numerator of $g$, and $D(\mathbf{v}_i, \mathbf{x}, \mathbf{u})$ is the denominator of $g$ (Figure \ref{fig:ident-flowchart}b). Note that $\mathbf{v}_i$, $\mathbf{x}$ and $\mathbf{u}$ are used to denote vector of vectors of fluxes for reaction $i$ ($\mathbf{v}_i$), metabolite ($\mathbf{x}$) and input ($\mathbf{u}$) concentrations, respectively, obtained from $p$ experiments denoted by the index $j = {1, 2, ..., p}$.
	\begin{align}\label{eq:theta-eq}
	\theta_k = g_k(\mathbf{v}_i, \mathbf{x}, \mathbf{u}) = \frac{N_k(\mathbf{v}_i, \mathbf{x}, \mathbf{u})}{D_k(\mathbf{v}_i, \mathbf{x}, \mathbf{u})}
	\end{align}

@@

	\begin{subequations}\label{eq:numerical_opt}
		\begin{align}
		\underset{\theta, \varepsilon}{min} & \sum_{j=1}^{n_p} \left|\varepsilon_j\right|\\
		& v_{i, j} - f_j(\mathbf{x}_j,\mathbf{\theta}, \mathbf{u}_j) \le \varepsilon_j && j=\{1, 2, ..., n_p\}\\
		& \theta_l \le \theta_j \le \theta_u && j=\{1, 2, ..., n_p\}
		\end{align}
	\end{subequations}

	Notice that the parameter values are bounded above and below by $\theta_u$ and $\theta_l$, respectively. These bounds can be specified to be arbitrarily large to include all possible parameter values.

@@

	The identifiability of each parameter based on each experiment with index $j = {1, 2, ..., n_E}$ is established based on the methodology described in Section \ref{sec:ident} (Figure \ref{fig:ident-flowchart}b), and demonstrated in Section \ref{sec:example}. Subsequently, for any flux $v_i$, and for any combination of $n_p$ experimental data sets, if the experimental concentrations and fluxes ($\mathbf{x}_j$ and $\mathbf{v}_j$, respectively, where $j = {1, 2,..., n_p}$) do not satisfy the condition for identifiability for any parameter $\theta_k$ in $\theta\in\mathbb{R}^{n_p}$ (Figure \ref{fig:ident-flowchart}b), then at least one of the $n_p$ experiments needs to be changed to make parameter $\theta_k$ identifiable. Consequently, the corresponding experiment cannot be used for estimating parameter $\theta_k$, and needs to be discarded from the set of all necessary experiments. Furthermore, another experiment from $j = {1, ..., n_E}$ needs to be selected to replace the discarded experiment such that parameter $\theta_k$ is identifiable. This process has to be repeated until all parameters in $\theta\in\mathbb{R}^p$ are identifiable for flux $v_i$. In doing so, we can arrive at a set of $n_p$ experiments that will always result in practically identifiable parameters for flux $v_i$. Note that if none of the $n_E$ pre-selected experiments satisfy the identifiability condition, then we can design an $(n_E+1)^{th}$ experiment that can replace one of the experiments that causes practical non-identifiability. This analysis can be performed for each flux in a metabolic network independent of all the other fluxes, making it theoretically scalable even to genome-scale models of metabolism.

@@

	\begin{figure}[!tbhp]
		\centering{\includegraphics[width=1.0\textwidth,height=.8\textheight,keepaspectratio]{figures/parameter_dist/v1_kcat_v2_v5_2_v3_1_parameter_dist}}
		\caption{Distribution of predicted parameter values when performing practical identifiability analysis using closed-form solutions for each parameter in flux a) $v_1$, b) $v_2$, c) $v_5$, and d)$v_3$. For $v_1$, we have assumed that enzyme concentration is available and have accordingly identified and estimated $k_1^{cat}$, as opposed to $V_1^{max}$. The parameter values for only the second root of $K_e^{fdp}$ in $v_5$ ($K_e^{fdp}(2)$) is shown, since $K_e^{fdp}(1)$ is not estimated by any combination of two experiments, and $V_e^{max}$ is estimated by all combinations. Only one of the two roots for $v_3$ is shown in panel d. The estimated data for the second root has a similar distribution to that of the first root. Data is generated using the Convenience Kinetic model for allosteric regulation for  $v_3$.}\label{fig:ident_values}
	\end{figure}

@@

	\begin{figure}[!tbhp]
		\centering{\includegraphics[width=0.8\textwidth,height=0.8\textheight, keepaspectratio]{figures/parameter_dist/v3_var_parameter_dist}}
		\caption{Distribution of predicted parameter values when performing practical identifiability analysis using closed-form solutions for each parameter in flux $v_3$. The globally identifiable parameter values of a)  $V_3^{max}$ and $K_3^{fdp}$ when $K_3^{pep}$ is held constant, and b) $V_3^{max}$ and $K_3^{pep}$ when $K_3^{fdp}$ is held constant.}\label{fig:v3_var_ck_values}
	\end{figure}

@@

	\begin{figure}[!tbhp]
		\centering{\includegraphics[width=1.0\textwidth,height=0.9\textheight,keepaspectratio]{figures/ident_exp_info/v1_kcat_v2_v5_2_exp_info}}
		\caption{The number of data combination from 21 different in silico experiments that can practically identify each parameter in fluxes a) $v_1$, b) $v_2$, and c) $v_5$ when there is no noise in the input experimental data. The percentage of total combinations of experimental data used for analysis (240 for $v_1$ and $v_2$, and 421 for $v_5$) that can identify each parameter is also specified. $v_1$, $v_2$ and $v_5$ require data from two experiments for analysis. The contribution of different experiment type towards identifying each parameter is shown in the spider plots for d) $v_1$, e) $v_2$ and f) $v_5$. The choice of perturbation chosen for the first experiment (blue) determines the choice of the second perturbation (green) required for identifying the parameters.}\label{fig:ident}
	\end{figure}

### 2018-06-11 ident/docs/sifigures.tex
changes to figures and addition of figure captions for sifigures

\section{Supplementary Figures}	
\begin{figure}[!tbhp]
	\centering{\includegraphics[width=1.0\textwidth,height=0.8\textheight, keepaspectratio]{figures/figure6/v1_kcat_ck_parameter_dist}}
	\caption{Distribution of predicted parameter values when performing practical identifiability analysis using closed-form solutions for each parameter in flux $v_1$ when there is no noise in the input experimental data. The top panel shows a violin plot of the distribution of parameter values. The means are indicated by a black line and the median values are indicated by a red line. The bottom panels show the corresponding distributions as histograms.}\label{fig:v1_kcat_ck_values}
\end{figure}

\begin{figure}[!tbhp]
	\centering{\includegraphics[width=1.0\textwidth,height=1.0\textheight, keepaspectratio]{figures/figure6/v1_vmax_ck_parameter_values}}
	\caption{Distribution of predicted parameter values when performing practical identifiability analysis using closed-form solutions for each parameter in flux $v_1$, which is described using as a Michaelis-Menten model, without using the enzyme concentration $E$ for identification when there is no noise in the input experimental data. Here $V_1^{max} = k_1^{cat}E$. The top panel shows a violin plot of the distribution of parameter values. The means are indicated by a black line and the median values are indicated by a red line. The bottom panels show the corresponding distributions as histograms.}\label{fig:v1_v1max_ck_values}
\end{figure}

\begin{figure}[!tbhp]
	\centering{\includegraphics[width=1.0\textwidth,height=1.0\textheight, keepaspectratio]{figures/figure1/v1_vmax_exp_info}}
	\caption{The number of data combination from 21 different in silico experiments that can practically identify each parameter in flux $v_1$, which is described using as a Michaelis-Menten model, without using the enzyme concentration $E$ for identification when there is no noise in the input experimental data. Here $V_1^{max} = k_1^{cat}E$. The percentage of total combinations of experimental data used for analysis (240 for $v_1$) that can identify each parameter is also specified. $v_1$ requires data from two experiments for analysis. The contribution of different experiment type towards identifying each parameter is shown in the spider plots for b) $v_1$. The choice of perturbation chosen for the first experiment (blue) determines the choice of the second perturbation (green) required for identifying the parameters.}\label{fig:v1_v1max_ck_ident}
\end{figure}

\begin{figure}[!tbhp]
	\centering{\includegraphics[width=1.0\textwidth,height=0.6\textheight, keepaspectratio]{figures/figure1/v3_ck_exp_info}}
	\caption{a) The number of data combination from 21 different in silico experiments that can practically identify each parameter in flux $v_3$ when there is no noise in the input experimental data. The percentage of total combinations of experimental data used for analysis (3360) that can identify each parameter is also specified. $v_3$ required data from three experiments for analysis. The contribution of different experiment type towards identifying each parameter is shown in the spider plots for b) $V_3^{max}$, c) $K_3^{fdp}$ and d) $K_3^{pep}$. The choice of perturbation chosen for the first experiment (blue) determines the choice of the second (green) and the third perturbation (yellow) required for identifying the parameters.}\label{fig:v3_1_ck_ident}
\end{figure}

\begin{figure}[!tbhp]
	\centering{\includegraphics[width=1.0\textwidth,height=0.3\textheight, keepaspectratio]{figures/figure1/v3_var_1_2_ck_ident_exp_info}}
	\caption{}\label{fig:v3_var_1_2_ck_ident}
\end{figure}

@@

\begin{figure}[!tbhp]
	\centering{\includegraphics[width=1.0\textwidth,height=0.6\textheight, keepaspectratio]{figures/figure2/v1_k1cat_exp_info}}
	\caption{Contribution of different experiment types towards identification of a) $k_1^{cat}$ and b) $K_1^{ac}$ in $v_1$ based on using data from two different experiments. Data from MWC model.}%\label{fig:figure2}
\end{figure}

>>>>

\section{Supplementary Figures}	
\begin{figure}[!tbhp]
	\centering{\includegraphics[width=1.0\textwidth,height=0.8\textheight, keepaspectratio]{figures/parameter_dist/v1_kcat_ck_parameter_dist}}
	\caption{Distribution of predicted parameter values when performing practical identifiability analysis using closed-form solutions for each parameter in flux $v_1$ when there is no noise in the input experimental data. The top panel shows a violin plot of the distribution of parameter values. The means are indicated by a black line and the median values are indicated by a red line. The bottom panels show the corresponding distributions as histograms.}\label{fig:v1_kcat_ck_values}
\end{figure}

\begin{figure}[!tbhp]
	\centering{\includegraphics[width=0.8\textwidth,height=0.8\textheight, keepaspectratio]{figures/parameter_dist/v2_parameter_dist}}
	\caption{Distribution of predicted parameter values when performing practical identifiability analysis using closed-form solutions for each parameter in flux $v_2$ when there is no noise in the input experimental data. The top panel shows a violin plot of the distribution of parameter values. The means are indicated by a black line and the median values are indicated by a red line. The bottom panels show the corresponding distributions as histograms.}\label{fig:v2_ck_values}
\end{figure}

\begin{figure}[!tbhp]
	\centering{\includegraphics[width=1.0\textwidth,height=0.8\textheight, keepaspectratio]{figures/parameter_dist/v3_parameter_dist}}
	\caption{Distribution of predicted parameter values when performing practical identifiability analysis using closed-form solutions for each parameter in flux $v_3$ when there is no noise in the input experimental data, and $v_3$ is expressed using the Convenience Kinetics model. The top panel shows a violin plot of the distribution of parameter values. The means are indicated by a black line and the median values are indicated by a red line. The bottom panels show the corresponding distributions as histograms.}\label{fig:v3_ck_values}
\end{figure}

\begin{figure}[!tbhp]
	\centering{\includegraphics[width=1.0\textwidth,height=0.8\textheight, keepaspectratio]{figures/parameter_dist/v5_parameter_dist}}
	\caption{Distribution of predicted parameter values when performing practical identifiability analysis using closed-form solutions for each parameter in flux $v_5$ when there is no noise in the input experimental data. The top panel shows a violin plot of the distribution of parameter values. The means are indicated by a black line and the median values are indicated by a red line. The bottom panels show the corresponding distributions as histograms.}\label{fig:v5_ck_values}
\end{figure}

\begin{figure}[!tbhp]
	\centering{\includegraphics[width=1.0\textwidth,height=1.0\textheight, keepaspectratio]{figures/parameter_dist/v1_vmax_ck_parameter_values}}
	\caption{Distribution of predicted parameter values when performing practical identifiability analysis using closed-form solutions for each parameter in flux $v_1$, which is described using as a Michaelis-Menten model, without using the enzyme concentration $E$ for identification when there is no noise in the input experimental data. Here $V_1^{max} = k_1^{cat}E$. The top panel shows a violin plot of the distribution of parameter values. The means are indicated by a black line and the median values are indicated by a red line. The bottom panels show the corresponding distributions as histograms.}\label{fig:v5_v1max_ck_values}
\end{figure}

\begin{figure}[!tbhp]
	\centering{\includegraphics[width=1.0\textwidth,height=1.0\textheight, keepaspectratio]{figures/ident_exp_info/v1_vmax_exp_info}}
	\caption{The number of data combination from 21 different in silico experiments that can practically identify each parameter in flux $v_1$, which is described using as a Michaelis-Menten model, without using the enzyme concentration $E$ for identification when there is no noise in the input experimental data. Here $V_1^{max} = k_1^{cat}E$. The percentage of total combinations of experimental data used for analysis (240 for $v_1$) that can identify each parameter is also specified. $v_1$ requires data from two experiments for analysis. The contribution of different experiment type towards identifying each parameter is shown in the spider plots for b) $v_1$. The choice of perturbation chosen for the first experiment (blue) determines the choice of the second perturbation (green) required for identifying the parameters.}\label{fig:v1_v1max_ck_ident}
\end{figure}

\begin{figure}[!tbhp]
	\centering{\includegraphics[width=1.0\textwidth,height=0.6\textheight, keepaspectratio]{figures/ident_exp_info/v3_ck_exp_info}}
	\caption{a) The number of data combination from 21 different in silico experiments that can practically identify each parameter in flux $v_3$ when there is no noise in the input experimental data. The percentage of total combinations of experimental data used for analysis (3360) that can identify each parameter is also specified. $v_3$ required data from three experiments for analysis. The contribution of different experiment type towards identifying each parameter is shown in the spider plots for b) $V_3^{max}$, c) $K_3^{fdp}$ and d) $K_3^{pep}$. The choice of perturbation chosen for the first experiment (blue) determines the choice of the second (green) and the third perturbation (yellow) required for identifying the parameters.}\label{fig:v3_1_ck_ident}
\end{figure}

\begin{figure}[!tbhp]
	\centering{\includegraphics[width=1.0\textwidth,height=0.8\textheight, keepaspectratio]{figures/parameter_dist/v3_var_k3fdp_parameter_dist}}
	\caption{Distribution of predicted parameter values when performing practical identifiability analysis using closed-form solutions for each parameter in flux $v_3$ (with constant $K_3^{pep}$) when there is no noise in the input experimental data. The top panel shows a violin plot of the distribution of parameter values. The means are indicated by a black line and the median values are indicated by a red line. The bottom panels show the corresponding distributions as histograms.}\label{fig:v3_var_k3fdp_values}
\end{figure}

\begin{figure}[!tbhp]
	\centering{\includegraphics[width=1.0\textwidth,height=0.8\textheight, keepaspectratio]{figures/parameter_dist/v3_var_k3pep_parameter_dist}}
	\caption{Distribution of predicted parameter values when performing practical identifiability analysis using closed-form solutions for each parameter in flux $v_3$ (with constant $K_3^{fdp}$) when there is no noise in the input experimental data. The top panel shows a violin plot of the distribution of parameter values. The means are indicated by a black line and the median values are indicated by a red line. The bottom panels show the corresponding distributions as histograms.}\label{fig:v3_var_k3pep_values}
\end{figure}

\begin{figure}[!tbhp]
	\centering{\includegraphics[width=1.0\textwidth,height=0.3\textheight, keepaspectratio]{figures/ident_exp_info/v3_var_exp_info}}
	\caption{}\label{fig:v3_var_1_2_ck_ident}
\end{figure}

@@
